Earth_microbiome_MS

### 2019-07-16 Earth_microbiome_MS copy.Rmd
updated

```{r Prevalence filtering}
#This method could be preferred to filter out plow-prevalence phyla

@@

#

@@

>>>>

#Prevalence Filtering
```{r Prevalence filtering}
#This method could be preferred to filter out plow-prevalence phyla
#Additionally, it could be useful to review potential sample data to verify the diversity of environments covered by this data set

@@

#Prune taxa using the previously set prevalence threshold
keepTaxa = rownames(prevdf)[(prevdf$Prevalence >= prevalence_threshold)]
github_filtered2 = prune_taxa(keepTaxa, githubdata_phyloseq)

#Display information
print(github_filtered2)

#display information about other tables for a comparison value. 
print(githubdata_phyloseq)
print(github_filtered)

```
Considering the comparison created above, I believe this method is not ideal unless the average prevalence of phyla within the data set is considered.

#Merge OTUs
```{r Merge OTUs}

@@

Methods of filtering?
